---
title: "Assigment - Naive Bayes DIY"
author:
  - Naana - Author
  - name reviewer here - Reviewer
date: March 24, 2022
output:
   html_notebook:
    toc: true
    toc_depth: 2
---

```{r}
#Install the packages. 
install.packages("tidyverse")
install.packages("tm")
install.packages("caret")
install.packages("wordcloud")
install.packages("e1071")
install.packages("dplyr")
```

```{r}
library(tidyverse)
library(tm)
library(caret)
library(wordcloud)
library(e1071)
library(dplyr)
```
---

Choose a suitable dataset from [this](https://github.com/HAN-M3DM-Data-Mining/assignments/tree/master/datasets) folder and train your own Naive Bayes model. Follow all the steps from the CRISP-DM model.


## Business Understanding
The fakenews dataset was chosen for this assignment. I will build a model in order to determine and predict if it is fake or real. 


## Data Understanding
```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/data-mining-s2y2122-EilisLerpetre/master/datasets/NB-fakenews.csv"
RawData <- read.csv(url)
```

## Data Preparation
```{r}
#Clean the data. 
RawData <- RawData[-2]
RawData <- RawData[-2]
RawData <- RawData[-2]
```

```{r}
#Label the codes.
RawData <- mutate(RawData,label = recode(label,"0" = "True","1" = "Fake"))

RawData$label <- RawData$label %>%  factor %>% relevel("Fake")
class(RawData$label)
```

```{r}
#Filter them.
Real <- RawData %>% filter(label == "fake")
Fake <- RawData %>% filter(label == "Fake")
```

```{r}
#Adding the text size and colors.
wordcloud(Fake$text,max.words = 25, scale = c(4,0.8), colors = c("Tomato1","Tomato2","Tomato3","Tomato")) 
wordcloud(Real$text,max.words = 25, scale = c(4,0.8),colors = c("Turquoise1","Turquoise2","Turquoise3","Turquoise")) 
```

```{r}
#Insepction.
rawCorpus <- Corpus(VectorSource(RawData$text)) 
inspect(rawCorpus[1:3]) 
```

```{r}
trainIndex <- createDataPartition(RawData$label,p = .75,list = FALSE,times = 1)
trainDataFrame <- RawData[trainIndex,] 
```

```{r}
cleanDTM <- rawCorpus %>% DocumentTermMatrix()
inspect(cleanDTM)
```

```{r}
trainCorpus <- cleanCorpus[trainIndex]
testCorpus <- cleanCorpus[-trainIndex]
trainDTM <- cleanDTM2[trainIndex, ]
testDTM <- cleanDTM2[-trainIndex, ]
```

```{r}
freqWords <- cleanDTM %>% findFreqTerms(10)
cleanDTM2 <- DocumentTermMatrix(cleanCorpus, list(dictionary = freqWords))
trainDTM <- DocumentTermMatrix(trainCorpus,list(dictionary = freqWords)) 

```

```{r}
convert_counts <- function(x) {
  x <- ifelse(x > 0, 1, 0) %>% factor(levels = c(0,1), labels = c("no", "yes"))}
nColsDTM <- dim(trainDTM)[2]
trainDTM <- apply(trainDTM, MARGIN = 2, convert_counts)
testDTM <- apply(testDTM, MARGIN = 2, convert_counts)
head(trainDTM[,1:10]) 
```

## Modeling, Evaluation
```{r}
nbayesm <- naiveBayes(trainDTM,trainDataFrame$label,laplace = 1) 
predVec <- predict(nbayesModel,testDTM) 
confusionMatrix(predVec,testDataFrame$label,positive = "Fake",dnn = c("Prediction","True")) 
```

reviewer adds suggestions for improving the model